Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
conclusino

In this paper, we presented an algorithm for generating an open
automaton representing the semantics of an open pNet.
We have also presented our implementation, which comprises two main
parts.
%\noteEM{doit pouvoir se reecrire de maniere plus simple et concise...}
%\hl{
  Firstly, we
  compute
%}
all the possible open transitions.
The algorithm combines the actions of subnets and
hole behaviors, which are then matched with the
synchronization vectors by the generated
predicate.  Some of the open transitions obtained at this
intermediate step, constructed in a structural manner from all
possible combinations of possible logical predicates, may
contain predicates which do not represent any possible concrete
instantiations. 
Secondly, to get rid of these useless transitions, we use the SMT solver Z3 for checking the
satisfiability of the predicate in each open transition. 
To this end, we encode into Z3 the representations of the action algebra and
the predicates before submitting them to the
Z3 solver. 
%
%\hl{%
%
In this paper, we used a running example, based on a BIP
architecture from an earlier nanosatellite case
study~\cite{CubETH-case-study}.  This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.  This encoding\mdash which we intend to formalise and prove
correct in a separate paper\mdash also opens the way for an extension
of BIP architectures with the transfer of data among variables of
different components.  Indeed, such data transfer can be easily
encoded using the predicates associated to synchronisation vectors in
open pNets.  The encoding of open transitions into SMTlib and the
availability of theories can guide the definition of such an extension.
%
%}
%
Our case-studies show that our encoding
successfully identifies the unsatisfiable open transitions and that
the resulting automata correctly reflect the expected 
movements of the encoded process expressions.

@@

\emph{Scaling up.} One important motivation of this work is to
attack the complexity of verification of realistic systems by a
composition and parametric approach. Still one may wonder if the price
for analysing our our symbolic transitions will not make the approach
innaplicable. As a first exercice in this direction, we tried a
slighly bigger example, assembling 2 Failure controlers. We give some
figures from this try in appendix~ref{}, showing that Z3 can check the
satisfiablility of a 90K open transitions in a metter of minutes.

@@

\newpage
\subsection{Scaling up: several subsystems on the same bus}

>>>>

The formal definitions and properties of the open pNets model were
published in \cite{henrio:Forte2016}. In this new work we describe an implementation of
the model and its semantics construction, including its interaction
with the Z3 SMT engine.
The implementation has two parts: the first is a finitary algorithm
that builds all possible combinations of synchronisations through the
pNet hierarchical structure. The result is a so-called
\emph{open-automaton}, which transitions contains predicates relating
the actions of the pNet holes and controllers. Some of the open
transitions obtained at this step,  may
contain predicates which do not represent any possible concrete
instantiations. 
In the second part of the tool we use the SMT solver Z3 for checking the
satisfiability of the predicate in each open transition. 
To this end, we encode into Z3 the representations of the action algebra and
the predicates before submitting them to the
Z3 solver. 
%
%\hl{%
%
In this paper, we used a running example, based on a BIP
architecture from an earlier nanosatellite case
study~\cite{CubETH-case-study}.  This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.  This encoding\mdash which we intend to formalise and prove
correct in a separate paper\mdash also opens the way for an extension
of BIP architectures with the transfer of data among variables of
different components.  Indeed, such data transfer can be easily
encoded using the predicates associated to synchronisation vectors in
open pNets.  The encoding of open transitions into SMTlib and the
availability of theories can guide the definition of such an extension.
%
%}
%
Our case-studies show that our encoding
successfully identifies the unsatisfiable open transitions and that
the resulting automata correctly reflect the expected 
movements of the encoded process expressions.

@@

\emph{Scaling up.} One important motivation of this work is to
attack the complexity of verification of realistic systems by a
composition and parametric approach. Still one may wonder if the price
for analysing our our symbolic transitions will not make the approach
innaplicable. As a first exercice in this direction, we tried a
slighly bigger example, assembling 2 Failure controlers. We give some
figures from this try in appendix~\ref{appendix:scalingup}, showing that Z3 can check the
satisfiablility of a 90K open transitions in a metter of minutes.

@@

\newpage
\subsection{Scaling up: several subsystems on the same bus}
\label{appendix:scalingup}
